### 2022-01-27 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_transfer@cab3bae55623b235e20fe3edb3a8d5cc5bc5c82a 🚀

In fig.~\ref{fig:concept}, we provide a methodological overview based on
learning the embedding of a metaweb of trophic interactions for European
mammals (known interactions; Maiorano et al., 2020a, 2020b) and, based
on phylogenetic relationships between mammals globally (\emph{i.e.},
phylogenetic tree Upham et al., 2019), infer a metaweb for the Canadian
mammalian species pool (using only a species list \emph{i.e.}
interactions are treated as unknown in this instance). Our case study
shows that phylogenetic transfer learning is an effective approach to
the generation of probabilistic metawebs. This showcases that although
the components (species) that make up the Canadian and European
communities may be \emph{minimally} shared (the overall species overlap
is less than 4\%), if the medium (proxy space) selected in the transfer
step is biologically plausible, we can still effectively learn from the
known network and make biologically relevant predictions of
interactions. Indeed, as we detail in the results, when validated
against known but fractional data of trophic interactions between
Canadian mammals, our model achieves a predictive accuracy of
approximately 91\%.

>>>>

In fig.~\ref{fig:concept}, we provide a methodological overview based on
learning the embedding of a metaweb of trophic interactions for European
mammals (known interactions; Maiorano et al., 2020a, 2020b) and, based
on phylogenetic relationships between mammals globally (\emph{i.e.},
phylogenetic tree Upham et al., 2019), infer a metaweb for the Canadian
mammalian species pool (using only a species list \emph{i.e.}
interactions are treated as unknown in this instance). Our case study
shows that phylogenetic transfer learning is an effective approach to
the generation of probabilistic metawebs. This showcases that although
the components (species) that make up the Canadian and European
communities may be \emph{minimally} shared (the overall species overlap
is less than 4\%), if the medium (proxy space) selected in the transfer
step is biologically plausible, we can still effectively learn from the
known network and make biologically relevant predictions of
interactions. Indeed, as we detail in the results, when validated
against the known (but fractional) data of trophic interactions present
between Canadian mammals, our model achieves a predictive accuracy of
approximately 91\%.
